Biologically-Constrained Region Merging for Connectome Reconstruction\\~\\\textit{Supplemental Material}

### 2018-03-19 papers/eccv2018/supplemental/classifier.tex

\subsection{Network Architecture}

We tested various architectures before deciding on the one we present in the paper. 
Each architecture uses VGG-style blocks (i.e. two convolutions of size $3\times3\times3$ followed by a max-pooling layer)~\cite{chatfield2014return}.
For the first two layers the max-pooling is anisotropic with reduction only in the $x$ and $y$ dimensions. 
The number of filters starts at 16 for the first block and doubles in each subsequent block.
Our architectures vary in the input size and number of layers. 
In all instances we extract a \SI{1200}{\nano\meter^3} region of interest and map the extracted voxels to the given input size. 
These input sizes correspond to specific output sizes from the last VGG block.

\begin{table}
	\scriptsize
	\centering
	\begin{tabular}{c c c c c c c}
		\hline
		\textbf{Depth} & \textbf{Input Size} & \textbf{No. Parameters} & \textbf{Output Size} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} \\ \hline
		      3        & (3, 18, 52, 52)     & 1,101,553               & (64, 3, 3, 3)        &                   &                    &  \\
		      3        & (3, 20, 60, 60)     & 2,313,969               & (64, 4, 4, 4)        &                   &                    &  \\
		      3        & (3, 22, 68, 68)     & 4,312,817               & (64, 5, 5, 5)        &                   &                    &  \\
		      3        & (3, 24, 76, 76)     & 7,294,705               & (64, 6, 6, 6)        &                   &                    &  \\
		      3        & (3, 26, 84, 84)     & 11,456,241              & (64, 7, 7, 8)        &                   &                    &  \\
		      3        & (3, 28, 92, 92)     & 16,994,033              & (64, 8, 7, 8)        &                   &                    &  \\
		      3        & (3, 30, 100, 100)   & 24,104,689              & (64, 9, 9, 9)        &                   &                    &  \\
		      4        & (3, 28, 92, 92)     & 1,404,913               & (128, 2, 2, 2)       &                   &                    &  \\
		      4        & (3, 32, 108, 108)   & 2,650,097               & (128, 3, 3, 3)       &                   &                    &  \\ \hline
	\end{tabular}
	\caption{The results of various network architectures trained on the Kasthuri data.}
	\label{table:input-size}
\end{table}

\subsection{Training Augmentation}

\subsection{Testing Augmentation}

>>>>

After generating the list of potential merge locations we extract a cubic region of interest around each.
We experimented with three different cube side lengths: $800 \textrm{nm}$, $1200 \textrm{nm}$, and $1600 \textrm{nm}$. 
Side lengths of $1200 \textrm{nm}$ performed better on the training and validation data on our network.

\vspace{1cm}

\noindent
\textbf{Network Architecture}
We tested various architectures before deciding on the one we present in the paper. 
Each architecture uses VGG-style blocks (i.e. two convolutions of size $3\times3\times3$ followed by a max-pooling layer)~\cite{chatfield2014return}.
For the first two layers the max-pooling is anisotropic with reduction only in the $x$ and $y$ dimensions. 
The number of filters starts at 16 for the first block and doubles in each subsequent block.
Our architectures vary in the input size and number of layers. 
In all instances we extract a \SI{1200}{\nano\meter^3} region of interest and map the extracted voxels to the given input size. 
These input sizes correspond to specific output sizes from the last VGG block.
For training we use the mean squared error loss function and optimize with SGD with Nesterov momentum.

\begin{table}
	\scriptsize
	\centering
	\begin{tabular}{c c c c c c c}
		\hline
		\textbf{Depth} & \textbf{Input Size} & \textbf{No. Parameters} & \textbf{Output Size} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} \\ \hline
		      3        & (3, 18, 52, 52)     & 1,101,553               & (64, 3, 3, 3)        & 91.30             & 58.06              & 92.81 \\
		      3        & (3, 20, 60, 60)     & 2,313,969               & (64, 4, 4, 4)        & 92.41             & 61.70              & 92.41 \\
		      3        & (3, 22, 68, 68)     & 4,312,817               & (64, 5, 5, 5)        & 92.33             & 61.49              & 92.34 \\
		      3        & (3, 24, 76, 76)     & 7,294,705               & (64, 6, 6, 6)        & 93.51             & 65.78              & 93.13 \\
		      \textbf{3}        & \textbf{(3, 26, 84, 84)}     & \textbf{11,456,241}              & \textbf{(64, 7, 7, 8)}        & \textbf{95.38}             & \textbf{74.43}              & \textbf{92.34} \\
		      3        & (3, 28, 92, 92)     & 16,994,033              & (64, 8, 7, 8)        & 91.87             & 59.70              & 94.22 \\
		      3        & (3, 30, 100, 100)   & 24,104,689              & (64, 9, 9, 9)        & 92.01             & 60.24              & 93.75 \\
		      4        & (3, 28, 92, 92)     & 1,404,913               & (128, 2, 2, 2)       & 91.70             & 60.24             & 85.94 \\
		      4        & (3, 32, 108, 108)   & 2,650,097               & (128, 3, 3, 3)       & 92.80             & 64.28              & 86.88 \\\hline
	\end{tabular}
	\caption{The results of various network architectures trained on the Kasthuri data.}
	\label{table:input-size}
\end{table}

\noindent
\textbf{Inference Augmentation}
Augmenting the data for inference increases the precision by 3.79\% and the accuracy by 0.64\%. 
Figure~\ref{fig:test-augmentation} shows the changes in the number of true positives, false positives, and false negatives as a function of the number of augmentations on the Kasthuri dataset.
The number of false positives decreases at first, falling below 200 after a second augmentation.
The gains become more gradual with the number of augmentations, leveling out around 175 false positives after 5 augmentations.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/Kasthuri-test-augmentation.png}
	\caption{The number of false positives decreases with our data augmentation scheme. The benefit of augmentation gradually decreases with the number of random examples.}
	\label{fig:test-augmentation}
\end{figure}

### 2018-03-19 papers/eccv2018/supplemental/skeletonization.tex

\subsection{Volume Downsampling}

\subsection{Node Generation}

\subsection{Edge Generation}

>>>>

\noindent
\textbf{Volume Downsampling}
We downsample the segmentation data to a resolution of $30$ nm in each direction. 
The skeletonization algorithm that we use takes as a parameter the minimum distance between joints in the skeleton~\cite{zhao2014automatic}.
When we downsample, we also reduce this minimum distance by the same rate.
We find that this produces expressive skeletons at a fraction of the computational cost. 
Table~\ref{table:skeleton} shows statistics comparing the skeletonization algorithm on 200 randomly chosen labels.

\begin{table}
	\scriptsize
	\begin{center}
		\begin{tabular}{c c c c c} \hline
			& \textbf{Average Time} &  \textbf{Skeleton Length} & \textbf{No. Branches} & \textbf{No. Endpoints} \\ \hline
			Full Resolution & 16.35s & 1,352,157nm & 9,858 & 1,068 \\
			Downsampled & 0.56s & 1,671,138nm & 9,359  & 1,824 \\ \hline
		\end{tabular}
	\caption{The results of the skeletonization algorithm on both the full resolution and the downsampled data. Downsampling the data provides expressive skeletons at a fraction of the computational cost.}
	\label{table:skeleton}
	\end{center}
\end{table}

\begin{figure}
	\begin{center}
		\includegraphics[width=0.45\linewidth]{./figures/node-threshold.png}
		\caption{The number of remaining nodes after increasing the threshold (blue) and the number of voxels excluded as a percent of the total volume (green).}
		\label{fig:node-pruning}
	\end{center}
\end{figure}

\noindent
\textbf{Node Generation}
We remove all nodes from the graph corresponding to labels with fewer than $t_{seg}$ voxels.
Figure \ref{fig:node-pruning} shows the results of varying $t_{seg}$ on two different quantities for the Kasthuri training volume. 
The blue line indicates the number of nodes remaining in the graph.
The rate of node reduction decreases for larger thresholds since there are fewer labels of larger size. 
The green line shows the percent of voxels with a label pruned from the graph.
Ideally this number is low since we want to remove small segments which do not contribute much to the overall volume.
This ``volume lost" grows at an increasing rate as the larger segments are removed. 
Based on these curves we set $t_{seg} = 20,000$ voxels.
With this threshold, we prune over half of the labels and only lose $1.5\%$ of the total volume.
